Proposal for improving content discovery through combining linked data and data mining techniques

### 2015-11-09 report/report.tex
Starting doing some conceptual diagrams.

\usepackage[Bjarne]{fncychap}
\begin{document}

@@

\chapter{System Design}
\chapter{Implementation}
\chapter{Evaluation}
\chapter{Conclusion}

>>>>

\usepackage[autosize]{dot2texi}
\usepackage[Bjarne]{fncychap}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\begin{document}

@@

\chapter{Background}

There is some existing work in the literature around data mining and the
semantic web.

\chapter{System Design}

\begin{figure}[h]
  \begin{center}
    \begin{dot2tex}[dot,pgf,options=-t math,scale=0.8]
      digraph g {
        rankdir=LR;

        node [shape=circle,margin="0,0"]
        edge [len=2];

        URI -> RDF [label="extract"];
        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Null content miner}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{dot2tex}[dot,pgf,options=-t math,scale=0.8]
      digraph g {
        rankdir=LR;
        nodesep=20;

        node [shape=circle,margin="0,0"]

        URI -> RDFa [label="fetch"];
        RDFa -> RDF [label="parse"];
        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Semantic web content miner}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{dot2tex}[dot,pgf,options=-t math,scale=0.8]
      digraph g {
        rankdir=LR;

        node [shape=circle,margin="0,0"]

        URI -> RDFa [label="parse"];
        URI -> Entities [label="extract"];
        URI -> Linked [label="scrape"];

        RDFa -> RDF [label="\cup"];
        Entities -> RDF [label="\cup"];
        Linked -> RDF [label="\cup"];

        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Maximal web content miner}
\end{figure}

\chapter{Implementation}
\chapter{Evaluation}
\chapter{Conclusion}
